---
title: "A linear model suggests ozone levels are stable"
output: github_document
---

> The bulk of the computation should have already happened upstream, and the
most of the code chunks in the report itself should be terse calls to tar_read()
and tar_load().

--https://books.ropensci.org/targets/files.html#literate-programming

### Setup

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(targets)
library(ggplot2)
```

### Introduction

[This report](https://github.com/2DegreesInvesting/ds.targets/blob/main/lm.md) summarizes our results, mostly as terse calls to `tar_read()`. 
For implementation details, see the underlying targets pipeline:

```{r}
writeLines(readLines("_targets.R"))
```

### Methods

To make this project easy to reproduce and share we built the R package [ds.targets](https://github.com/2DegreesInvesting/ds-targets). You can
install it from GitHub with:

```r
# install.packages("devtools")
devtools::install_github("2DegreesInvesting/ds.targets")
```

To clean the raw data we removed observations where `Ozone` values were missing.

```{r}
# Source code
ds.targets::clean

# Before
raw_data <- tar_read(raw)
any(is.na(raw_data$Ozone))

# After
clean_data <- tar_read(data)
any(is.na(clean_data$Ozone))
```

To explored changes in `Ozone` through time we use a linear model.

### Results

Here are our results:

```{r}
tar_read(lm_plot)
```

### Conclusion

We see no evidence that Ozone changes through time.
